Draft

### 2024-06-26 Draft.Rmd
Martes tarde
Mercredi midi

>>>>

# Draft for part after 25 June

```{r}
fun_diag <- function(x,y){
  (x + y) <= 1000
}
```

```{r}
random_points$elt <- random_points$rho2/pi
```

```{r}
est_ratio2 <- sum(random_points$elt)
```

```{r}
integral2(fun_diag, 0, 1000, 0, 1000)
```

```{r}
integrate(function(y) {
  sapply(y, function(y){
    integrate(function(x){
      fun_ratio(x,y)}, 0, 1000)
    })
  }, 0, 1000)

```

# Draft for variance in No_cell.Rmd

```{r}
# var_est <- function(f){
#   random_points$carre <- (random_points$rho1)^2
#   est_carre <- sum((random_points$carre)/pi)
# }
```
